Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Getting figures in order.

\begin{figure}
\centering
\include{bench-overview}
\caption{Overview performance comparison between baseline and
  optimized analyzer (entries of \text{{\small $t$}} mean timeout, and \text{{\small $m$}} mean out of memory).}
\label{fig:bench-overview}
\end{figure}

@@

Our implementation of the analysis used in the evaluation is roughly
3500 lines of Racket code.
%% 400 lines for the core, 700 lines for
%% abstraction over optimizations, 1500 lines for primitives and standard
%% list operations, 700 lines for instantiations to different
%% optimizations and 300 for parsing and macro transformers.

\begin{figure*}
\begin{center}
\includegraphics[width=6in]{rel-time.ps}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=3.2in]{abs-time.ps}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.2in]{state-per-sec.ps}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.2in]{peak-mem.ps}
\end{center}
\end{figure}

>>>>

We use the following set of benchmarks:
\begin{figure}
\centering
\include{bench-overview}
\caption{Overview performance comparison between baseline and
  optimized analyzer (entries of \text{{\small $t$}} mean timeout, and \text{{\small $m$}} mean out of memory).}
\label{fig:bench-overview}
\end{figure}

@@

%% 400 lines for the core, 700 lines for
%% abstraction over optimizations, 1500 lines for primitives and standard
%% list operations, 700 lines for instantiations to different
%% optimizations and 300 for parsing and macro transformers.

Figure~\ref{fig:bench-overview} gives an overview of the benchmark
results in terms of absolute time, space, and speed between the
baseline and most optimized analyzer.  Figure~\ref{fig:bench-all}
plots the factors of improvement over the baseline for each
optimization step.

\begin{figure*}
\begin{center}
  \includegraphics[width=6.5in]{all-relative-memory.ps}

  (a) Peak memory usage

  \vspace{1em}
  \includegraphics[width=6.5in]{all-relative-speed.ps}

  (b) Rate of state transitions

  \vspace{1em}
  \includegraphics[width=6.5in]{all-relative-time.ps}

  (c) Total analysis time
\end{center}
\caption{Factors of improvement over baseline for each step of
  optimization.}
\label{fig:bench-all}
\end{figure*}
